Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-06 paper/paper.tex
performance

>>>>

The other comparison must be made between Anglican and other
probabilistic programming environment. \cite[pp. 32 -- 33]{P16} 
provides a comparison of Anglican to an older, interpreted
version of Anglican~\cite{WVM14}, and Probabilistic
Scheme~\cite{PW14} on a rather complicated inference task of
program synthesis. According to this comparison, Anglican is at
least 10 times faster than the older interpreted version, and
almost as fast as Probabilistic Scheme which uses inference
engine implemented in C. In addition, \cite[p. 171]{SGG15}
compares Anglican to a DSL for probabilistic programming in
Haskell and to Probabilistic C~\cite{PW14} on two simple
probabilistic programs. Anglican shows similar performance
to the Haskell implementation of Sequential Monte
Carlo~\cite{DFG+01} and scales better with the number of
particles. Given the simplicity of the programs used in the
evaluation, this comparison is a confirmation that the flexible
checkpoint and trampoline based interaction between Anglican
program and inference engine does not introduce any noticeable
overhead compared to more rigid designs.
